---
title: "My Reproducible Report"
author: "A forward thinking researcher"
date: '2023-01-17'
output: 
  html_document: default
  word_document: default
  pdf_document: default
---

## Overview 
This file provides a quick look at how each component of an R Markdown file works together to produce an integrated report.

Remember, R Markdown allows us to:

-   **Combine narriative text, code, and output** into a single document
-   Incorporate mathematical expressions or equations
-   And render/export the .Rmd file to a variety of output file formats!
-   The YAML header specified in this `.Rmd` file enables us to render the output to:
    -   A Microsoft Word document (`.docx`)
    -   A `pdf` file
    -   Or `html` file

## Load packages
In this code chunk, we are loading some relevant package libraries. By using the `include = FALSE` in our chunk options, we are telling the `.Rmd` file to exclude the code/output from the exported document.

```{r, include=FALSE}
# Packages
library(tidyverse)
library(gapminder)
```


## Create a plot in the below code chunk
Below we create a faceted figure using the gapminder dataset. We use the chunk options to specify the figure output height and width, as well as to create a figure caption. Notice that we can also use markdown syntax to format the caption text (e.g., **bold face text**)

```{r, fig.height=7, fig.width=10, fig.cap="**Life expecetancy over time by country, stratified by continent.**", fig.pos="center"}

# Create life expectancy by year figure
ggplot(gapminder, aes(x = year, y = lifeExp, color = country)) +
  geom_line(show.legend = FALSE) +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(1950, 2010),
    breaks = seq(1950, 2010, 10)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(20, 90),
    breaks = seq(20, 90, 10)
  ) +
  labs(x = "Year", y = "Life Expectancy at Birth (Years)") +
  facet_wrap(~ continent) +
  theme_bw() +
  theme(
    axis.text = element_text(face = "bold", color = "black"),
    axis.text.x = element_text(angle = 45, vjust = 0.6),
    axis.title = element_text(face = "bold"),
    strip.text = element_text(face = "bold"),
    panel.spacing.x = unit(1.5, "lines"),
    panel.spacing.y = unit(1.5, "lines")
  )
```


### Some examples of how you can embed quantitative statments into your file with LaTeX.

-   Enclosing the expression in pairs of two dollar signs (`$$`..`$$`) generates a stand-alone equation.
$$
\begin{equation}
\hat{Y}_i = \hat{\beta}_0 + \hat{\beta}_1 X_i + \hat{\epsilon}_i
\end{equation}
$$
-   In contrast, wrapping the expression in a pair of single dollar signs (`$`..`$`) creates an in-line quantitative expression.

<br>

-   This is some text with an in-line equation like $\hat{Y}_i = \hat{\beta}_0 + \hat{\beta}_1 X_i + \hat{\epsilon}_i$. Pretty cool, right?


<br>
<br>